%-------------------------
% Resume in Latex  --  FRONTEND-leaning variant
% Author : Jake Gutierrez  |  License : MIT
% Content: Yogesh Chauhan
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Yogesh Chauhan} \\ \vspace{1pt}
    New Delhi, India \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 7838780046 ~ \href{mailto:chauhanyogesh950@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{chauhanyogesh950@gmail.com}} ~
    \href{https://yogeshchauhan.dev}{\raisebox{-0.2\height}\faGlobe\ \underline{yogeshchauhan.dev}} ~
    \href{https://www.linkedin.com/in/yogeshchauhan-dev}{\raisebox{-0.2\height}\faLinkedin\ \underline{yogeshchauhan-dev}}  ~
    \href{https://github.com/Yogesh0627}{\raisebox{-0.2\height}\faGithub\ \underline{Yogesh0627}}
    \vspace{-8pt}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{Frontend-focused engineer with 2 years building fast, maintainable \textbf{React + TypeScript} apps, plus the APIs behind them. Lead frontend engineer on a multi-tenant HR SaaS, where I built three React/TypeScript portals with \textbf{Redux Toolkit}, route-level code-splitting, skeleton loaders, and a typed API service layer, backed by a Vitest test suite. I care about performance, clean component architecture, and shipping polished UI end-to-end.}
\vspace{-6pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {WorkCompanion LLP}{Oct 2024 -- Present}
      {Software Engineer}{Gurugram, Haryana}
      \resumeItemListStart
        \resumeItem{Built three \textbf{React/TypeScript} portals (Employee, Manager, HR) as lead frontend engineer: \textbf{Redux Toolkit} state management, route-level \textbf{code-splitting} (React.lazy + Suspense), skeleton loaders, and a \textbf{typed API service layer} for consistent error handling; added a \textbf{Vitest} test suite.}
        \resumeItem{Shipped features end-to-end from MongoDB models to REST APIs to Redux/React UI on a multi-tenant PMS SaaS (\textbf{$\sim$1,500 commits across 3 repositories}).}
        \resumeItem{Built AI-powered UI including an \textbf{OpenAI GPT-4.1-mini} appraisal-question generator (prompt + PDF/DOCX/CSV inputs) and \textbf{tl;dv}-driven performance-review summaries.}
        \resumeItem{Led a backend optimization program that raised documented code quality \textbf{4.5$\rightarrow$8.6/10} and cut authentication latency \textbf{76\% (145$\rightarrow$35ms)} with Redis caching, plus \textbf{44 MongoDB indexes}.}
        \resumeItem{Delivered core PMS modules end-to-end including the Appraisal Cycle Engine, 360$^{\circ}$ Feedback, RBAC, Timeline Engine, Question Bank, Notifications, and Excel Import/Export.}
      \resumeItemListEnd
  \vspace{8pt}

    \resumeSubheading
      {Agami Technologies}{June 2024 -- Oct 2024}
      {Software Specialist}{Greater Noida, Uttar Pradesh}
      \resumeItemListStart
        \resumeItem{Built UI features across the \textbf{MEVN stack} (MongoDB, Express, \textbf{Vue.js}, Node.js) with Socket.io for real-time updates; resolved \textbf{398+ bugs} with QA and product teams.}
        \resumeItem{Delivered \textbf{7+ core features} and contributed to \textbf{24+ system improvements}, optimizing UI behavior and usability.}
        \resumeItem{Integrated \textbf{OpenAI} into the \textbf{BeGenieus} platform: GPT chat, AI-powered image generation, and AI-driven features across multiple modules.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-9pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Candor} $|$ \emph{Next.js, TypeScript, MongoDB, Gemini, Redis}}{\href{https://candor-cyan.vercel.app}{\underline{Live}} $|$ \href{https://github.com/Yogesh0627/anonymous-message-app}{\underline{Code}}}
          \resumeItemListStart
            \resumeItem{\textbf{AI growth loop:} Gemini-powered safety moderation + an AI Feedback Coach that clusters anonymous feedback into a trackable growth plan, with AI reply suggestions streamed to senders.}
            \resumeItem{Polished \textbf{Next.js} UI (dark/light theming, shadcn/ui, skeleton loading, admin console), with a real-time inbox via Server-Sent Events and full production SEO.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{SQLPlay} $|$ \emph{React, TypeScript, Vite, SQLite (WebAssembly)}}{\href{https://sqlplay.vercel.app}{\underline{Live}} $|$ \href{https://www.npmjs.com/package/sqlplay}{\underline{npm}} $|$ \href{https://github.com/Yogesh0627/sqlplay}{\underline{Code}}}
          \resumeItemListStart
            \resumeItem{A zero-setup, H2-Console-style SQL playground with a query editor, schema browser, and ER-diagram view, running a real SQLite database 100\% in the browser via WebAssembly; \textbf{published on npm}.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{InsightBlog} $|$ \emph{React, Vite, TanStack Query, Hono, Prisma}}{\href{https://insightblog-one.vercel.app}{\underline{Live}} $|$ \href{https://github.com/Yogesh0627/Full_Stack_Project}{\underline{Code}}}
          \resumeItemListStart
            \resumeItem{\textbf{React + Vite} publishing platform with an AI writing assistant (Gemini), a multi-source Trending Hub, and author/admin analytics dashboards; TanStack Query for data-fetching and a serverless Hono backend.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-9pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, JavaScript (ES2022+), HTML/CSS, SQL} \\
     \textbf{Frontend}{: React, Next.js, Redux Toolkit, TanStack Query, Vue.js, Tailwind CSS, MUI, shadcn/ui, Vite} \\
     \textbf{Backend}{: Node.js, Express.js, Hono, Cloudflare Workers, AWS S3, REST APIs, SSE, Socket.io, Zod, JWT / NextAuth} \\
     \textbf{Databases \& Caching}{: MongoDB / Mongoose, PostgreSQL / Neon, MySQL, Prisma, Redis / Upstash} \\
     \textbf{AI}{: Google Gemini, OpenAI (GPT), Vercel AI SDK} \\
     \textbf{Tools \& Testing}{: Git, GitHub Actions (CI/CD), Vitest, Jest, Playwright, ESLint, Prettier} \\
    }}
 \end{itemize}
\vspace{-9pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ganga Institute of Technology \& Management (GITAM)}{Aug. 2021 -- Aug. 2024}
      {Bachelor of Technology (B.Tech), Mechanical Engineering}{Jhajjar, Haryana}
  \resumeSubHeadingListEnd

\end{document}
